\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-04-07 prelims.tex
.

For the purpose of falsification, $\System$ is viewed as a black-box
equipped with a forward simulation map $\simulate^{\System}:
(\HybridStates, \vu, t) \mapsto \HybridStates$.  A simulation step
computes the unique reachable state $\vx \in \HybridStates$ in time
$t$ from a given state input pair $(\vx,\vu)$.  We formalize this
using the notion of time parameterized reachability relations
$\reach{t, \vu}_\System \subseteq \HybridStates \times \HybridStates$
detailed in~\cite{zutshi2014multiple}.
Hence, $\vy=\simulate^{\System}(\vx,u,t)$ \emph{iff} $\vx \reach{t,u}
\vy$.
% Given the hybrid state space $\vx\in\HybridStates$ and input space $u
% \in\Inputs$ and time step $t$, it computes the unique successor state
% $\vy=\simulate^{\System}(\vx,u,t)$ such that $\vx \reach{t,u} \vy$.

>>>>

For the purpose of falsification, $\System$ is viewed as a black-box
equipped with a forward simulation map $\simulate^{\System}:
(\vx, \vu, t) \mapsto \vx$.  A simulation step
involves computing the unique reachable state $\vx \in \HybridStates$ in time
$t$ from a given state input pair $(\vx,\vu)$.  We formalize this
using the notion of time parameterized reachability relations
$\reach{t, \vu}_\System \subseteq \HybridStates \times \HybridStates$
detailed in~\cite{zutshi2014multiple}. Finally, $\vx'=\simulate^{\System}(\vx,u,t)$ \emph{iff} $\vx \reach{t,u} \vx'$.
% Given the hybrid state space $\vx\in\HybridStates$ and input space $u
% \in\Inputs$ and time step $t$, it computes the unique successor state
% $\vy=\simulate^{\System}(\vx,u,t)$ such that $\vx \reach{t,u} \vy$.
